HMM Model development

### 2020-05-07 dev/hmm_model_devel.Rmd
WIP using brms to have predictors for HMM

improving_data <- data.frame(day = data$observed$times, patient = data$observed$patients, improving = data$true$true_improving) %>% filter(improving)

data.frame(day = data$observed$times, patient = data$observed$patients, breathing = data$true$true_base_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + geom_tile(data = improving_data, width = 1, height = 0.1, fill = "gray") + ggtitle("True - gray lines for improving")

data.frame(day = data$observed$times, patient = data$observed$patients, breathing = data$observed$obs_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + ggtitle("Observed")
```

@@

sbc_res$params %>% filter(grepl("rates", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("sensitivity", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("other_observations_probs", param_name)) %>% plot_sbc_params()

@@

```{r}
library(brms)
test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
f <- cbind(a,b) ~ 0 + (0 + x2 | a | x1)
make_stancode(f, data = test_data)
make_standata(f, data = test_data)
```

>>>>

improving_data <- data.frame(day = data$observed$times, patient = data$observed$series, improving = data$true$true_improving) %>% filter(improving)

data.frame(day = data$observed$times, patient = data$observed$series, breathing = data$true$true_base_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + geom_tile(data = improving_data, width = 1, height = 0.1, fill = "gray") + ggtitle("True - gray lines for improving")

data.frame(day = data$observed$times, patient = data$observed$series, breathing = data$observed$obs_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + ggtitle("Observed")
```

@@

sbc_res$params %>% filter(grepl("mu", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("sensitivity", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("other_observations_probs", param_name)) %>% plot_sbc_params()

@@

```{r}
library(brms)
```

```{r}
data <- hmm_simulator(10, 20, 2, use_noisy_states = TRUE)
cc <- make_stancode_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data)

model2 <- stan_model(model_code = cc)

prep_data <- make_data_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data)

all_data <- c(make_standata( make_brms_formula_hmm(data$observed_structured$formula), data = prep_data$brmsdata),
              prep_data$standata)

sampling(model2, data = all_data)

```{r}

test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
# f <- cbind(a,b) ~ 0 + (0 + x2 | a | x1)
# make_stancode(f, data = test_data)
# make_standata(f, data = test_data)

stan_llh.rate_hmm <- function( ... ) {
  ""
}

.family_rate_hmm <- function() {

}

ff <-

make_stancode(a ~ 0 + x2, family = ff, data = test_data)
